Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-20 inst/examples/20170201-manuscript.Rmd
ok

# Title count per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
# Sort by biggest publication decade
#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
ord <- as.character((npub %>% group_by(publisher) %>% 
                        summarise(decade = median(publication_decade)) %>% 
                        arrange(decade))$publisher)
npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))

# Translate
npub$publisher <- gsub("ja poika", "and son", npub$publisher)
npub$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub$publisher)

>>>>

# Title count per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)

# Translate
npub$publisher <- gsub("ja poika", "and son", npub$publisher)
npub$publisher <- gsub("J.C. Frenckell and son", "Frenckell, Johan Christopher & Son", npub$publisher)
npub$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub$publisher)
npub$publisher <- gsub("Johan Christopher Frenckell's widow", "Frenckell, Johan Christopher's widow", npub$publisher)

#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
# Sort by biggest publication decade
#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher

ord <- as.character((npub %>% group_by(publisher) %>% 
                        summarise(decade = median(publication_decade)) %>% 
                        arrange(decade))$publisher)
npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
